Guidelines for reliable and reproducible functional enrichment analysis

### 2021-09-01 example.Rmd
assembling the figs

@@

>>>>

dir.create("images")

@@

pdf("images/fcs_ora1.pdf",width=4,height=4)
plot(euler(v1),quantities = TRUE, main="FCS vs ORA")
dev.off()

pdf("images/orabg1.pdf",width=4,height=4)
plot(euler(v2),quantities = TRUE, main="Effect of inappropriate background* (whole genome)")
dev.off()

pdf("images/oracomb1.pdf",width=4,height=4)
plot(euler(vx),quantities = TRUE, main="combining up and down genes and whole genome bg*")
dev.off()

### 2021-09-01 manuscript_draft.Rmd
assembling the figs

library(DiagrammeR)
grViz("digraph flowchart {
      # node definitions with substituted label text
      node [fontname = Helvetica, shape = rectangle]        
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab3 [label = '@@3']
      tab4 [label = '@@4']
      tab5 [label = '@@5']
      tab6 [label = '@@6']
      tab7 [label = '@@7']
      tab8 [label = '@@8']
      tab9 [label = '@@9']
      tab10 [label = '@@10']
      tab11 [label = '@@11']
      tab12 [label = '@@12']
      tab13 [label = '@@13']

@@

>>>>

library(tidyverse)
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)

grViz("digraph flowchart {
      # node definitions with substituted label text
      node [fontname = Helvetica, shape = rectangle]        
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab3 [label = '@@3']
      tab4 [label = '@@4']
      tab5 [label = '@@5']
      tab6 [label = '@@6']
      tab7 [label = '@@7']
      tab8 [label = '@@8']
      tab9 [label = '@@9']
      tab10 [label = '@@10']
      tab11 [label = '@@11']
      tab12 [label = '@@12']
      tab13 [label = '@@13']

@@

tmp <- grViz("digraph flowchart {
      # node definitions with substituted label text
      node [fontname = Helvetica, shape = rectangle]        
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab3 [label = '@@3']
      tab4 [label = '@@4']
      tab5 [label = '@@5']
      tab6 [label = '@@6']
      tab7 [label = '@@7']
      tab8 [label = '@@8']
      tab9 [label = '@@9']
      tab10 [label = '@@10']
      tab11 [label = '@@11']
      tab12 [label = '@@12']
      tab13 [label = '@@13']

      # edge definitions with the node IDs
      tab1 -> tab2  -> tab4 -> tab5 -> tab6 -> tab7;
      tab2 -> tab3 ;
      tab1 -> tab9 -> tab10;
      tab5 -> tab13   ;
      tab9 -> tab11 -> tab12 -> tab13 -> tab8 ; 
      }
      [1]: 'PMC keyword search (2019): 2941 results'
      [2]: '200 PMC articles selected'
      [3]: '14 articles excluded'
      [4]: '235 analyses screened and cross-checked'
      [5]: 'data entry to spreadsheet'
      [6]: 'data analysis in R'
      [7]: 'summary charts'
      [8]: 'integration with journal and article metrics'
      [9]: 'additional 1300 PMC articles selected'
      [10]: '118 articles excluded'
      [11]: '1395 analyses screened'
      [12]: 'data entry to spreadsheet'
      [13]: 'data analysis in R'
")

tmp2 <- capture.output(rsvg_pdf(charToRaw(export_svg(tmp)),'images/flowchart.pdf'))
